Brownian Dynein Model

### 2015-10-25 latex/derivation.tex
Change bothbound angle schemes and add lots of stuff to derivation.tex. Make sure to check if the Xt/Yt derivatives are right.

@@

\begin{figure}[h!]
  \caption{Key lengths and angles in bothbound dynein model.}
  \centering
    \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
\end{figure}

\section{Cartesian Coordinate Derivation}

By the law of cosines:
\begin{align}
  L_n &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})}\\
  L_f &= \sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})}\\
\end{align}

We want to find cartesian coordinates in terms of $L_n$ and $L_f$.\\

Also by the law of cosines, we see that:
\begin{align}
  \Theta_{1} &= \cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg) \\
  \Theta_{2} &= \pm\cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg) \\
\end{align}

We use these equations to solve for our nm (near motor) coordinates:

\begin{align}
  X_{nm} &= L_{s}*\cos(\Theta_{1}+\Theta_{2}) =
     L_{s}*\cos\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
  Y_{nm} &= L_{s}*\sin(\Theta_{1}+\Theta_{2}) =
     L_{s}*\sin\Bigg(\cos^{-1}\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)
     \pm \cos^{-1}\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)\Bigg) \\
\end{align}

We then use the trigonometric rules $$\cos\Big(cos^{-1}(a)\pm
cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}$$
and $$\sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}$$ to simplify our expressions:

\begin{align}
  X_{nm} &= L_{s}\Bigg( \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\Big) \mp \sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
  Y_{nm} &= L_{s}\Bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm \frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg) \\
\end{align}

We simplify further...

\begin{align}
  X_{nm} &= \Big(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\Big)\Big(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\Big) \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

\begin{align}
  X_{nm} &= \frac{1}{4LL_s}\Big(L^2+L_{n}^2-L_{f}^2\Big)\Big(L_{s}^2+L_{n}^2-L_{t}^2\Big)\big(L_n \big)^{-2} \mp L_s\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2}\\
  Y_{nm} &= \frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{n}}\sqrt{1-\bigg(\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\bigg)^2} \pm L_s\frac{L^2+L_{n}^2-L_{f}^2}{2LL_{n}}\sqrt{1-\bigg(\frac{L_{s}^2+L_{n}^2-L_{t}^2}{2L_{s}L_{n}}\bigg)^2} \Bigg)\\
\end{align}

Now we derive with respect to time. Things which are time-dependent: $L_n, L_f$.

\begin{align}
  \dot{X}_{nm} =
  &-\frac{\text{Ls} \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4
   \text{Ls}^2 \text{Ln}(t)^2}} \left(\frac{\text{Ln}'(t)
   \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{2 L^2
   \text{Ln}(t)^3}-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right) \left(2
   \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t) \text{Lf}'(t)\right)}{2 L^2
   \text{Ln}(t)^2}\right)}{2
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2
   \text{Ln}(t)^2}}} - \\
  &\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{2 L \text{Ls}
   \text{Ln}(t)^3}\\
  &-\frac{\text{Ls}
   \sqrt{1-\frac{\left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)^2}{4 L^2 \text{Ln}(t)^2}}
   \left(\frac{\text{Ln}'(t) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{2
   \text{Ls}^2 \text{Ln}(t)^3}-\frac{\text{Ln}'(t)
   \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{\text{Ls}^2 \text{Ln}(t)}\right)}{2
   \sqrt{1-\frac{\left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)^2}{4 \text{Ls}^2
       \text{Ln}(t)^2}}}\\
  & +\frac{\text{Ln}'(t) \left(L^2-\text{Lf}(t)^2+\text{Ln}(t)^2\right)}{2
   L \text{Ls} \text{Ln}(t)}+\frac{\left(2 \text{Ln}(t) \text{Ln}'(t)-2 \text{Lf}(t)
   \text{Lf}'(t)\right) \left(\text{Ln}(t)^2+\text{Ls}^2-\text{Lt}^2\right)}{4 L \text{Ls}
   \text{Ln}(t)^2}
\end{align}

This is becoming really ugly! I think I want to try another thing. Tomorrow I'll try and implement a different angle scheme and see if it works out easier...this is not tenable. The advantage to this scheme is that it avoids ambiguity, but it is also really really complicated. And even this model has ambiguity in that certain angles could have positive/negative values, so the C code will have to have memory and guess which value is correct. So I think it would be good to choose a simpler ambiguous model and code in ambiguity-resolution to the C code.\\

We can also use the law of cosines to find an expression for $\Theta_{1}$:

\begin{align}
   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
\end{align}

We use this to find the value of $X_{t}$:

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
\end{align}

To find $Y_{t}$ we do something similar:

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &=  \\
  X_{t}  &= \frac{L^2+L_n^2-L_f^2}{2L} \\
  X_{fm} &=  \\
  X_{fb} &= L \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &=  \\
  Y_{t}  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
  Y_{fm} &=  \\
  Y_{fb} &= 0
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \\
  \dot{X}_{t } &= \frac{L^2+2L_n\dot{L}_n-2L_f\dot{L}_f}{2L} \\
  \dot{X}_{fm} &= \\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                          
  \dot{Y}_{nb} &= 0 \\                                         
  \dot{Y}_{nm} &= \\
  \dot{Y}_{t}  &= \frac{L_n}{2\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2}} * \big(\frac{(-L^2L_n^{-2}+\dot{L}_n - 2L_f\dot{L}_nL_n^{-1} + L_f^2L_n^{-2}}{2L}\big) - think this is rite?\\
  \dot{Y}_{fm} &= \\
  \dot{Y}_{fb} &= 0 \\
\end{align}

>>>>

\allowdisplaybreaks

@@

%% \begin{figure}[h!]
%%   \caption{Key lengths and angles in bothbound dynein model.}
%%   \centering
%%     \includegraphics[width=0.7\textwidth]{../figures/bothbound_model.png}
%% \end{figure}

\section{Derivation of bothbound tail coordinates}

\begin{align*}
  \theta_1 &= \cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right)\\
  \theta_2 &= \cos^{-1}\left(\frac{L}{2L_t}\right)\\
  L &= \sqrt{(X_{fm}-X_{nm})^2+(Y_{fm}-Y_{nm})^2}\\
\end{align*}

\subsection{$X_t$}
\begin{align*}
  X_t &= X_{nm} + L_t\cos(\theta_1 \pm \theta_2)\\
  &= X_{nm} + L_t\cos\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \cos\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = ab \mp \sqrt{1-a^2}\sqrt{1-b^2}\\
  &= X_{nm} + L_t\left(\frac{X_{fm}-X_{nm}}{2L_t} \mp \sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{1 - \frac{L^2}{4L_t^2}}\right)\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2L}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2}\sqrt{4L_t - L^2}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{1}{2}\sqrt{(Y_{fm}-Y_{nm})^2}\sqrt{\frac{4L_t}{L^2} - 1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2L}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} -1}\\
  &= \frac{X_{fm}+X_{nm}}{2} \mp \frac{Y_{fm}-Y_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} -1}\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + 2BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))(L_s\cos(\theta_{nb})) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2} * \\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} -1}\\\\
  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
\end{align*}

\subsection{$Y_t$}
\begin{align*}
  Y_t &= Y_{nm} + L_t\sin(\theta_1 \pm \theta_2)\\
  &= Y_{nm} + L_t\sin\left(\cos^{-1}\left(\frac{X_{fm}-X_{nm}}{L}\right) \pm \cos^{-1}\left(\frac{L}{2L_t}\right) \right)
  \hspace*{1in} \sin\Big(cos^{-1}(a)\pm cos^{-1}(b)\Big) = \sqrt{1-a^2}b\pm a\sqrt{1-b^2}\\
  &= Y_{nm} + L_t\left(\frac{L}{2L_t}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{L}\sqrt{1 - \frac{L^2}{4L^2_t}}\right)\\
  &= Y_{nm} + \frac{L}{2}\sqrt{1 - \frac{\left(X_{fm}-X_{nm}\right)^2}{L^2}} \pm \frac{X_{fm}-X_{nm}}{2L}\sqrt{4L_t^2 - L^2}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{L^2 - \left(X_{fm}-X_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{L^2} - 1}\\
  &= Y_{nm} + \frac{1}{2}\sqrt{\left(Y_{fm}-Y_{nm}\right)^2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{\left(X_{fm}-X_{nm}\right)^2 + \left(Y_{fm}-Y_{nm}\right)^2} - 1}\\
  &= \frac{Y_{fm} + Y_{nm}}{2} \pm \frac{X_{fm}-X_{nm}}{2}\sqrt{\frac{4L_t^2}{X_{fm}^2 + X_{nm}^2 + Y_{fm}^2 + Y_{nm}^2 -2X_{fm}X_{nm} -2Y_{fm}Y_{nm}} - 1}\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{B^2 + L_s^2\cos^2(\theta_{fb}) + BL_s\cos(\theta_{fb}) + L_s^2\cos^2(\theta_{nb}) + L_s^2\sin^2(\theta_{fb}) + L_s^2\sin^2(\theta_{nb}) -2(B + L_s\cos(\theta_{fb}))L_s\cos(\theta_{nb}) -2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2} *\\
  &\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb})\cos(\theta_{nb}) - 2L_s^2\sin(\theta_{fb})\sin(\theta_{nb})} - 1}\\\\
  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
\end{align*}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the bothbound Dynein model.\\
\begin{align}
  X_{nb} &= 0\\
  X_{nm} &= L_s\cos(\theta_{nb})\\
  X_{t}  &= \frac{B + L_s\cos(\theta_{fb}) + L_s\cos(\theta_{nb})}{2} \mp \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  X_{fm} &= B + L_s\cos(\theta_{fb})\\
  X_{fb} &= B \\
\end{align}

\begin{align}
  Y_{nb} &= 0 \\
  Y_{nm} &= L_s\sin(\theta_{nb})\\
  Y_{t}  &= \frac{L_s\sin(\theta_{fb}) + L_s\sin(\theta_{nb})}{2} \pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}\\
  Y_{fm} &= L_s\sin(\theta_{fb})\\
  Y_{fb} &= 0\\
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= -L_s\sin(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{X}_{t } &= \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + -L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2} \mp \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} - L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}\\
  &\pm \frac{L_s\sin(\theta_{fb})-L_s\sin(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2} \left(-2BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})\right)}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + 2BL_s\cos(\theta_{fb}) - 2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} -1}}\\
  \dot{X}_{fm} &= -L_s\sin(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{X}_{fb} &= 0
\end{align}

\begin{align}                                                                  
  \dot{Y}_{nb} &= 0 \\                                 
  \dot{Y}_{nm} &= L_s\cos(\theta_{nb})\dot{\theta}_{nb}\\
  \dot{Y}_{t}  &= \frac{L_s\cos(\theta_{fb})\dot{\theta}_{fb} + L_s\cos(\theta_{nb})\dot{\theta}_{nb}}{2}\pm \frac{-L_s\sin(\theta_{fb})\dot{\theta}_{fb} + L_s\sin(\theta_{nb})\dot{\theta}_{nb}}{2}\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1} \\
 &\pm \frac{B + L_s\cos(\theta_{fb}) - L_s\cos(\theta_{nb})}{2}\frac{\frac{-4L_t^2}{\left(2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})\right)^2}-BL_s\sin(\theta_{fb})\dot{\theta}_{fb} + 2BL_s\sin(\theta_{nb})\dot{\theta}_{nb} + 2L_s^2\sin(\theta_{fb} - \theta_{nb})(\dot{\theta}_{fb}+\dot{\theta}_{nb})}{2\sqrt{\frac{4L_t^2}{2L_s^2 + B^2 + BL_s\cos(\theta_{fb}) -2BL_s\cos(\theta_{nb}) - 2L_s^2\cos(\theta_{fb} - \theta_{nb})} - 1}}\\
  \dot{Y}_{fm} &= L_s\cos(\theta_{fb})\dot{\theta}_{fb}\\
  \dot{Y}_{fb} &= 0 \\
\end{align}
